---
title       : "Data Computing: Chapter 6"
description : Exercises
---

--- type:NormalExercise lang:r xp:10 skills:1 key:f3dd9b22a2
## Problem 6.1

In the previous chapter, you graphed a summary of the `CPS85` data like that shown in the figure: counts of people working in each sector of the economy. In this exercise, you're going to add new aethetics to the bars and facet the graph.

*** =instructions
- Set the "fill" color for the bars based on whether the person belongs to a `union`. To do this, fill in the blank following `fill:` with the variable that is to be mapped to the fill aesthetic.
- Facet the graph based on `sex`. To do this, complete the formula argument to the `facet_grid()` function.

*** =pre_exercise_code
```{r}
library("statisticalModeling")
library("ggplot2")
data(CPS85, package = "mosaicData")
gf_counts( ~ sector, data = CPS85))
```

*** =hint
In this exercise, you need only replace the blanks `___` with the appropriate variable. Everything else is all set.


*** =sample_code
```{r}
library("statisticalModeling")
library("ggplot2")
data(CPS85, package = "mosaicData")
gf_counts( ~ sector + fill:___, data = CPS85) + facet_grid( ~ ___)
```


*** =solution
```{r}
library(statisticalModeling)
library(ggplot2)
data(CPS85, package = "mosaicData")
gf_counts( ~ sector + fill:union, data = CPS85) + facet_grid( ~ sex)
```

*** =sct
```{r}
test_function("gf_points")
test_function("facet_grid")
success_msg("In general, aesthetics such as color, size, fill, etc. are mapped to variables by adding into the formula a component in the form `aesthetic:variable`.")
```

--- type:NormalExercise lang:r xp:10 skills:1 key:1ac4fd86fb
## Problem 6.2

The figure shows the graphic you made in the last exercise. There's a U-shaped pattern in the graph: at low birth rates, as birth rate increases from one country to another the death rate goes down. But for high birth rates, increasing birth rate is associated with increasing death rate.

The tragic factor behind this pattern is overall health in each country. In countries with good health, the death rate is largely shaped by the age distribution in the country. In such countries, a high birth rate is associated with a younger population, hence one with a lower death rate. (Example: Mexico, which has a much lower death rate than its neighbor, the US) In countries with poor health, the death rate is high. But at the same time, women in those countries have many children who, often, have a high mortality rate.

The graphic, as it is, does not incorporate the overall health of countries, so it's not possible to compare the hypothesis in the previous paragraph with the data.

*** =pre_exercise_code
```{r}
library("ggplot2")
data(CountryData, package = "DataComputing")
gf_point(death ~ birth, data = CountryData)
```

*** =instructions
- Life expectancy (`life`) is one measure of a country's overall health.
- Map `life` to the glyph size in the plot. Do this by adding on to the formula: `+ size:life`.
- Examine the plot carefully to see if the graphic supports the hypothesis given above.
- Now, rather than using size to represent `life`, use color. You do this by modifying the formula in the obvious way, `color:life` in place of `size:life`.


*** =hint
The formula will have to parts on the right-hand side of the tilde: `death ~ birth + size:life`. 

*** =sample_code
```{r}
# attach the package with the gf_ functions
library(statisticalModeling)
# grab the CountryData table
data(CountryData, package = "DataComputing")

# map the variable life to the size aesthetic
gf_point(death ~ birth + size:___, data = CountryData)

# Make another graphic in which you
# map the variable life to the color aesthetic
gf_point(death ~ birth + ___:life, data = CountryData)
```

*** =solution
```{r}
library(statisticalModeling)
data(CountryData, package = "DataComputing")

gf_point(death ~ birth + size:life, data = CountryData)
gf_point(death ~ birth + color:life, data = CountryData)
```

*** =sct
test_student_typed("size:life", not_typed_msg = "Did you make one plot where you map the variable `life` to the glyph `size`?")
test_student_typed("color:life", not_typed_msg = "Did you make a plot where you mapped the variable `life` to the glyph `color`?")
test_student_typed("data *= *CountryData", fixed = FALSE, not_typed_msg = "Remember to set the value of the argument `data = ` to the data table being used.")
success_msg("Many design choices in graphic design are a matter of mapping variables to the aesthetic properties of glyphs.  In the `gf_` function formulas, the variable on the left of the tilde determines the variable mapped to y. The first variable on the right sets the variable to be mapped to x. Then other aesthetics are set by pairs in the form aethetic:variable, for instance `size:life` or `color:life`.")

--- type:NormalExercise lang:r xp:10 skills:1  key:29b4042c3a
## Problem 6.3

In the previous chapter, you made a box-and-whisker plot like that shown in the graphic.

*** =pre_exercise_code
```{r}
library("statisticalModeling")
library("ggplot2")
data(CPS85, package = "mosaicData")
gf_boxplot(wage ~ sector, data = CPS85)
```

*** =solution
```{r}
library("statisticalModeling")
data(CPS85, package = "mosaicData")

gf_boxplot(wage ~ sector + fill:sex, data = CPS85) + facet_grid( . ~ union)
```


*** =sct
```{r}
test_student_typed("~ *union", fixed = FALSE,
                   not_typed_msg = "To facet by `union`, you'll need to give the appropriate formula as an argument to `facet_grid()`.")
test_student_typed("fill:sex", not_typed_msg = "Remember to map `sex` to the `fill` aesthetic in the formula for `gf_boxplot()`.")
success_msg("You've made the graphic! Whether it's a good graphic or not depends on what you're trying to show. This one puts the wages of men and women next to each other for each sector, which is good for comparing wages between the sexes. But for other purposes it might be appropriate to put side by side the wages for union and non-union workers, or to facet by `sector`. Different arrangements of the data can reveal different aspects of the data.")
```













