---
title       : "Data Computing: Chapter 7"
description : Exercises
---

--- type:NormalExercise lang:r xp:10 skills:1 key:3f1c2bd7bb
## Problem 7.1: Pipes and data verbs

A data verb is a function that takes a data table as input and produces a data table as output. `sample_n()` is a data verb that performs a very simple tasks: it draws a random sample of cases from the input data table and presents that sample as the output.

The sample code shows a simple data-wrangling expression using `sample_n()`. Run that expression several times to see that the output differs from run to run: the sample is random! The `size =` argument to `sample_n()` sets how big the sample will be.

*** =instructions
- First, re-write the expression using pipe notation.
- Second, arrange that the output of the expression is stored in an object named `My_sample`.
- Finally, arrange the argument to `sample_n()` so that there are 10 cases in the output.

*** =pre
```{r}
library(dplyr)
```

*** =solution
```{r}
library("dplyr")
# read in the Births78 data table
data(Births78, package = "mosaicData")

# select a random sample of 3 cases
sample_n(Births78, size = 3)

# First, re-write the above to use pipe notation
Births78 %>% sample_n(size = 3)

# Second, re-write the above to save the output in My_sample
My_sample <- Births78 %>% sample_n(size = 3)

# Last, arrange for there to be 10 random cases in My_sample
My_sample <- Births78 %>% sample_n(size = 10)
```

*** =sample_code
```{r}
# read in the Births78 data table
data(Births78, package = "mosaicData")

# select a random sample of 3 cases
sample_n(Births78, size = 3)

# First, re-write the above to use pipe notation


# Second, re-write the above to save the output in My_sample


# Last, arrange for there to be 10 random cases in My_sample

```

*** =hint
Two things change in pipe notation:
- The original expression began with a data verb whose first argument was a data table. The pipe expression begins with the input data table followed by a pipe symbol `%>%`.
- In the pipe expression, the data verb comes after the pipe.
- In the pipe expression, the data table is **not** given as an argument inside the parentheses. Instead, the pipe is telling the data verb which data table to take as input.

*** =sct
```{r}
test_student_typed("size *= *10", fixed = FALSE,
                   not_typed_msg = "Did you change the sample size to 10?")
test_student_typed("Births78 *%>% *sample_n", fixed = FALSE,
                   not_typed_msg = "Remember, it's `data_table %>% data_verb`.")
test_student_typed("My_sample *(=|<-)", fixed = FALSE,
                   not_typed_msg = "Did you assign the output to `My_sample`?")
```

--- type:NormalExercise lang:r xp:10 skills:1  key:09597021b5
## Problem 7.2: The summarise() data verb

One of the most widely used data verbs is `summarise()`. Like all data verbs, `summarise()` takes as input a data table. It performs a reduction on the data table, for example calculating the sum of the values in a variable.

Of course, you have to tell `summarise()` what summaries you want to perform. All summaries involve a "reduction verb", a function like `mean()` or `sum()` that takes the values in a variable and reduces them to a single value.

We'll use the `Births78` data in this exercise. This data table gives the number of births in the US on each day of the year in 1978. The variable `births` gives the number of babies born on each day.

*** =instructions

- You will use the data verb `summarise()` and will pipe the `Births78` data table to be the input to `summarise()`. You will also give, as an argument to `summarise()` an expression that calculates the total `sum()` of `births` 
- Give the argument the name `total` so that the output data table has a variable named `total`.

*** =pre
```{r}
data(Births78, package = "mosaicData")
library("dplyr")
```


*** =solution
```{r}
data(Births78, package = "mosaicData")
library("dplyr")

Births78 %>% summarise(total = sum(births))
```

*** =sample_code
```{r}
# provide access to Births78
data(Births78, package = "mosaicData")
# the data wrangling package
library("dplyr")

Births78 %>% summarise(___)
```

*** =hint
The reduction verb `sum()` takes a variable as input and provides as output the sum of all the values in that variable. `sum(births)` is an expression that can be given as an argument to the data verb `summarise()` to instruct it to evaluate the expression on the data table piped in as input. Naming the argument, e.g. `summarise(total = sum(births))` gives the name `total` to the corresponding output of `summarise()`.

*** =sct
```{r}
test_student_typed("total *=", fixed = FALSE, not_typed_msg = "Remember to give the argument to `summarise()` the name `total`.")
test_function("sum")
test_function("summarise")
test_student_typed("sum( *births *)", fixed = FALSE, not_typed_msg = "You need to give `sum` a variable name.")
success_msg("Not too hard, once you get the hang of it.")
```



--- type:NormalExercise lang:r xp:10 skills:1  key:8a50b0fc03
## Problem 7.3: Groupwise summaries

Wrangling often involves computing summaries for different groups of cases. The `group_by()` data verb allows you to specify how to divide the cases into groups so that `summarise()` and other data verbs know what to do. 

Typically, you will define groups based on the level of one or more a variables. For instance, the `wday` variable in `Births78` tells which day of the week --- Sunday, Monday, ... --- each of the dates corresponds to.

*** =instructions
- Pipe `Births78` into `group_by()`. Give `group_by()` the argument `wday`, so that groups are defined by the day of the week.
- The output of `group_by()` should be piped into `summarise()`. Arrange `summarise()` to have an argument named `total` that sums the number of `births`.
- The result should be a separate sum, named `total`, for each day of the week.

*** =pre
```{r}
data(Births78, package = "mosaicData")
library(dplyr)
```

*** =solution
```{r}
data(Births78, package = "mosaicData")
library("dplyr")
Births78 %>%
  group_by(wday) %>%
  summarise(total = sum(births))
```

*** =hint
Pipe `Births78` into `group_by(wday)`. Then, pipe the output of `group_by(wday)` to a `summarise()` function whose argument computes the quantity `total = sum(births)`. 

*** =sample_code
```{r}
data(Births78, package = "mosaicData")
library("dplyr")
Births78 %>%
  group_by(___) %>%
  summarise(___ = sum(___))
```

*** =sct
```{r}
test_function("group_by")
test_function("sum")
test_function("summarise")
correct_msg("Note that the output contains *only* the variables used for grouping and the variables created by `summarise()`.")
```

--- type:MultipleChoiceExercise lang:r xp:10 skills:1 key:5c7130b69f
## Problem 7.4: group_by() with other data verbs

The `group_by()` function simply marks the data table as having groups (specified by the arguments to `group_by()`). Those groups can be used by any data verb, not just `summarise()`.

In this exercise, you're going to pipe the output of `group_by()` into `sample_n()`. Examine the output and tried to figure out how `sample_n()` used the groups marked by `group_by()`.

Which way did `sample_n()` use the groups?

*** =instructions
- It randomly picked a group and selected only cases within that group.
- It operated separately on each group and collected the results for all the groups together into the output.
- It ignored the groups.

*** =pre
```{r}
data(Births78, package = "mosaicData")
library("dplyr")
```

*** =sample_code
```{r}
data(Births78, package = "mosaicData")
library("dplyr")

Births78 %>% 
  group_by(wday) %>%
  sample_n(size = 2)
```



Another exercise: how many are there? Compare nrow to summarise(n())

--- type:NormalExercise lang:r xp:10 skills:1   key:3001619592
## Problem 7.4: Groupwise summaries

Sum `Births78` by day `wday`.

--- type:NormalExercise lang:r xp:10 skills:1   key:f94b90f2af
## Problem 7.5: Groups defined by multiple variables

Group by `wday` and `month`


--- type:NormalExercise lang:r xp:10 skills:1  key:8fc75bae48
## Problem 7.6: Transformations

Where we'll use a transformation verb, e
You also provide as an argument to `summarise()` a data-reduction statement.

