---
title       : "Data Computing: Chapter 3"
description : Exercises
---

--- type:NormalExercise lang:r xp:10 skills:1   key:bb80c301aa
## Problem 3.1.A

*** =instructions
Fix the statement so that it has the proper form.

*** =hint
- Literal names, like `"Prince"`, should be in quotes.
- A pipe can never be at the start of a line.
- A data table should be given before the first pipe (`%>%`).
- When a data table is piped into a function, you should not also include the table as an explicit first argument, so `BabyNames %>% filter(name == "Prince")` instead of `BabyNames %>% filter(BabyNames, name == "Prince")`.

*** =pre
```{r}
library(DataComputing)
Prince <- "Fred"
```

*** =sample_code
```{r}
Just_the_Princes <- 
  %>% 
  filter(BabyNames, name == Prince)
```

*** =solution
```{r}
Result <-
  BabyNames %>%
  filter(name == "Prince")
```

*** =sct
```{r}
test_student_typed("BabyNames *%>%", fixed = FALSE,
                   not_typed_msg = "Remember, the data table `BabyNames` should come before the first type.")
```
