---
title       : "Data Computing: Chapter 8"
description : Exercises
---

--- type:NormalExercise lang:r xp:10 skills:1 
## Problem 8.1: Making a graphics frame

In previous exercises, you used a formula-based interface to the `ggplot2` system for graphics. That formula-based interface is intended to be easy for getting started with making simple graphics. In these exercises, you'll practice with the `ggplot` interface itself.

The `ggplot()` function is used to define a the graphics frame. The frame it makes is blank, ready to have additional layers of glyphs added to it. The typical arguments to `ggplot()` are:

1. A data table, given as the first argument or piped into `ggplot()`.
2. An `aes()` statement which constructs the mapping from variables in the data table to the `x` and `y` aesthetics, that is, the frame itself.

*** =pre_exercise_code
```{r}
data(CountryData, package = "DataComputing")
library("ggplot2")
library("dplyr")
CountryData %>% ggplot(aes(x = death, y = life))
```

The graphic shows a (blank) frame constructed by `ggplot()`. (We'll add layers to this blank frame in the exercises that follow.)

*** =instructions
- Read from the graph the variables that have been mapped to the x and y aethetics.
- Fill in the blanks in order to construct a command that will reproduce the blank frame.

*** =solution
```{r}
data(CountryData, package = "DataComputing")
library("ggplot2")
CountryData %>% ggplot(aes(x = life, y = death))
```

*** =sample_code
```{r}
# Provide access to CountryData
data(CountryData, package = "DataComputing")

# Attach the ggplot2 package
library("ggplot2")

# Fill in the blanks ...
CountryData %>%
  ggplot(aes(x = life, y = death))
```

*** =hint
As you can see, `life` is being mapped to the x aesthetic, `death` to the y aesthetic. It will seem a bit odd at first, but remember to use `aes()` as a function, given as an argument to `ggplot()`, and map the aesthetics by giving appropriate arguments to `aes()`.

*** =sct
```{r}
test_function("aes")
test_function("ggplot")
test_student_typed("x *= *life", fixed = FALSE, not_typed_msg = "Did you map `life` to the x-aesthetic?")
test_student_typed("y *= *death", fixed = FALSE, not_typed_msg = "Did you map `death` to the y-aesthetic?")
success_msg("Good. A blank frame isn't good for much. We'll add glyphs, labels, and such in the exercises that follow.")
```



## Adding a layer

## Faceting

## Mapping an aesthetic in the layer

## Adding x- and y-axis labels


## Hints from the formula interface

How to get the formula interface to print out the corresponding ggplot command.

