---
title       : "Data Computing: Chapter 2"
description : Exercises
---

--- type:NormalExercise lang:r xp:10 skills:1  key:4350d12adb
## Problem 2.1.A

*** =instructions
Fix the syntax so that the command works.

*** =sample_code
```{r}
ralph <- sqrt 100
```

*** =solution
```{r}
ralph <- sqrt(100)
```

*** =hint
The arguments to functions must *always* be in parentheses.

*** =sct
```{r}
test_object("ralph", incorrect_msg = "You were supposed to calculate the square root of 100.")
test_student_typed("sqrt\\( *100 *\\)", fixed = FALSE, 
                   not_typed_msg = "We want you to do the sqrt() function to do the calculation. It's not the answer we're concerned with here but that process of getting to the answer.")
success_msg("Good.")
```

--- type:NormalExercise lang:r xp:10 skills:1  key:b99a32ad13
## Problem 2.1.B

*** =instructions
Fix the syntax so that the command works.

*** =sample_code 
```{r}
message <- Say 'hello' to her, please.
```

*** =solution
```{r}
message <- "Say 'hello' to her, please."
```

*** =hint
Text meant to be taken literally should be formatted as a character string. That is, it should be in quotes like this: `"a character string"`

*** =sct
```{r}
test_object("message", incorrect_msg = "You shouldn't change the contents of the string, just put it in quotes.")

success_msg("Good.")
```

--- type:NormalExercise lang:r xp:10 skills:1 
## Problem 2.1.C

*** =instructions
Fix the syntax so that the command works.

*** =sample_code 
```{r}
y <- sin[2 pi]
```

*** =solution
```{r}
y <- sin(2 * pi)
```

*** =hint
There are two errors here. One is about the punctuation for arguments: it's not square brackets. The other is about multiplication. In R, multiplication must be explicitly stated with `*`.

*** =sct
```{r}
test_object("y", incorrect_msg = "Are you sure you set y to be the sin of `2 * pi`?")

success_msg("Good.")
```