---
title       : "Data Computing: Chapter 1"
description : Exercises
attachments :
  slides_link : https://s3.amazonaws.com/assets.datacamp.com/course/teach/slides_example.pdf
---


--- type:NormalExercise lang:r xp:50 skills:1  key:94fe242b81
## Problem 1.1 

DataCamp is a system that lets you type and modify and lets your work be evaluated so that hints can be given.

In this exercise, you are going to intentionally provide a wrong answer so that you see how the DataCamp interface works

*** =instructions
- Change the value of `second_thing` so that the sum of `first_thing` and `second_thing` is 40.  But **intentionally make a mistake** so that the sum is **50**.
- Press submit. You'll be told that you're wrong.
- Now correct your answer your answer so that the sum is 40.

*** =pre
```{r}
.target <- 40
```

*** =solution
```{r}
first_thing <- 10
second_thing <- 30  # change this

# their sum
first_thing + second_thing
```

*** =sample_code
```{r}
first_thing <- 10
second_thing <- 10  # change this

# their sum
first_thing + second_thing
```

*** =sct
```{r}
test_object("first_thing", 
            incorrect_msg = "The instructions didn't say anything about changing `first_thing`. Change its value back to 10.")
test_object("second_thing", 
            incorrect_msg = "Feedback messages look like this. Your `second_thing` is not set to a value that will make the sum with `first_thing` equal to 40.")
success_msg("When you have correctly solved the problem, you'll get a success message and you're ready to go on to the next problem. Of course, you can also navigate to the next problem without having solved the first one, and perhaps go back to the first one when you have the time.")
```


--- type:NormalExercise lang:r xp:50 skills:1  key:b439b5d3fe
## Problem 1.2

When you work in RStudio, you'll be creating markdown documents and putting your commands in those documents. The documents will also include narrative, graphics, and so on. (This will be introduced in Chapter XXXXX 3?). But in DataCamp you will be creating a "script" that consists only of commands. With DataCamp, there are three ways to execute the commands you give:

1. Type a command at the R Console
2. Type or edit a command in the script window. Highlight it and press command/return. If the command has multiple lines, you'll need to highlight all the lines --- you can't run them one at a time.
3. Press "Submit Answer". This sends everything in the script, highlighted or not, for evaluation.



*** =instructions
- The script has been pre-populated with some R commands. Ignore these for now. Instead, you're going to give commands in the R Console:
    - Put this command at the prompt (`>`) in the R Console: `x <- 25`. Execute it. Another prompt will be shown.
    - Put this command in the R Console: `sqrt(x)`. Execute it. You'll get the response `[1] 5` and another prompt will be shown.
- Back to the Script. Highlight the first command and press CMD-RETURN. Look for the response in the R Console.
- Also in the script ... Highlight the several lines of the second command. Press CMD-RETURN. Again you'll see the response in the R console.
- Try highlighting just the first line in the second command and pressing CMD-RETURN. You'll get a message in the console, "unexpected end of input."
- Finally, for the third way of running the commands. Press "Submit Answer." All of the commands in the script will be run. The results will be checked, and you'll get a message about how you did from the DataCamp system.


*** =sample_code
```{r}
# A single-line command
library(DataComputing)

# A multi-line command.
WorldCities %>%
  group_by(country) %>%
  summarise(total = sum(population)) %>%
  filter(total > 10000000) %>%
  arrange(desc(total))
```
*** =solution
```{r}
# A single-line command
library(DataComputing)

# A multi-line command.
WorldCities %>%
  group_by(country) %>%
  summarise(total = sum(population)) %>%
  filter(total > 10000000) %>%
  arrange(desc(total))
```

*** =sct
```{r}
success_msg("Ready to move on ....")
```

--- type:NormalExercise lang:r xp:50 skills:1 key:7edaec5a41
## Problem 1.3

In your work with *Data Computing*, you will be using the `ggplot2` package for making graphics.  The sample code shows a few lines from a data table named `Diamonds`. The `ggplot()` command plots price against size (`carat`) for different cuts of diamonds.

*** =instructions
- Execute each of the two commands in the sample code to verify that it is working.
- Once you have done this, modify the `ggplot()` command so that the `clarity` variable is used instead of `cut`. If you read the existing command carefully, you should be able to figure out how to do this.

*** =hint
The phrase `color = cut` instructs `ggplot()` to set the color of each dot according to the value of the variable `cut`. So change `cut` to `clarity`.

*** =pre_exercise_code
```{r}
library(ggplot2)
```

*** =sample_code
```{r}
# Show the first few lines of the data table
head(diamonds)

# Plot out some of the data
ggplot(diamonds, 
       aes(x = carat, y = price, color = cut)) + 
  geom_point()

# Modify the above to display the diamonds' clarity rather than cut.

```

*** =solution
```{r}
ggplot(diamonds, 
       aes(x = carat, y = price, color = clarity)) + 
  geom_point()
```

*** =sct
```{r}
test_student_typed(c("color *= *clarity"), fixed = FALSE, 
              not_typed_msg = "Remember to set color = clarity."  )
success_msg("Good. Even though you may never have programmed before, you were still able to figure it out!")
```

--- type:NormalExercise lang:r xp:50 skills:1 key:8553b72780
## Problem 1.4

The sample code finds the mean price for each cut of diamonds. Look through the code to see where the variables `price` and `cut` appear.

*** =instructions
- Modify the code to find the mean weight (`carat`) for each clarity of diamonds. 


*** =hint
Notice that the variable `cut` appears in the `group_by()` part of the expression. You can change `cut` to `clarity` to get the job done.

*** =pre-exercise-code
```{r}
library(dplyr)
library(ggplot2)
```

*** =sample_code
```{r}
# load the packages
require(dplyr)
data(diamonds, package = "ggplot2")

# do the wrangling
diamonds %>%
  group_by(cut) %>%
  summarise(val = mean(price))
```

*** = solution
```{r}
# load the packages
require(dplyr)
data(diamonds, package = "ggplot2")

# do the wrangling
diamonds %>%
  group_by(clarity) %>%
  summarise(val = mean(carat))
```


*** =sct
```{r}
test_student_typed("group_by\\( *clarity *\\)", fixed = FALSE, 
                   not_typed_msg = "Have you changed the variable name in `group_by(cut)` to `clarity`?")
success_msg("It looks like you're ready to move on.")
```