---
title       : "Data Computing: Chapter 5"
description : Exercises
---

--- type:NormalExercise lang:r xp:10 skills:1   key:36737e0973
## Problem 5.1

R is an open-source platform. As such, many people can contribute their ideas and the community of users can choose among them. One of the areas where this plays out is in graphics. There are many ways to draw graphics using R.

The graphics system we use in this course is provided by the `"ggplot2"` package. This is one of many extremely popular packages written by [Hadley Wickham](https://en.wikipedia.org/wiki/Hadley_Wickham), the chief scientist at RStudio.

The functions provided by `"ggplot2"` constitute what can be called an Application Programming Interface (API). Many people find the `"ggplot2"` API hard to figure out at first. In the *Data Computing* textbook, a menu-driven alternative is provided.

In these exercises, you'll use yet another alternative interface provided by the `"statisticalModeling"` package. This interface, implemented by functions whose names start with `gf_`, allows you to use model formulas to specify `"ggplot2"` graphics.

A *formula* in R is an expression built around the `~` ("tilde") sign. It enables you to describe a relationship among variables. For instance: `wage ~ age` means "wage versus age."

Use the `library()` function to attach the `"statisticalModeling"` package. Then ask for help on one of the functions: `help(gf_point)`. The help documentation should show up in another window in your browser.

*** =hint
The formula will be `death ~ life`.

*** =instructions
- Use `library()` to attach the `"statisticalModeling"` package, which provides the `gf_` interface to `"ggplot2"`.
- Use `data()` to load the `CountryData` table from `"DataComputing"`.
- `gf_point()` makes a scatter plot: one point for each case.
    - plot the death rate (`death`) versus birth rate (`birth`) the `CountryData`. This means that `death` should be on the left side of the formula and `birth` on the right side.

*** =sample_code
```{r}
library(___)
data(CountryData, package = "DataComputing")

gf_point(__formula__, data = __datatable__)
```

*** =solution
```{r}
library("statisticalModeling")
data(CountryData, package = "DataComputing")

gf_point(death ~ birth, data = CountryData)
```

*** =sct
```{r}
test_student_typed("death *~ *birth", fixed = FALSE, not_typed_msg = "The first argument should be a formula")
test_student_typed("data *= *CountryData", fixed = FALSE, not_typed_msg = "Use `CountryData` as the value for the `data =` argument.")
success_msg("Good!")
```

--- type:NormalExercise lang:r xp:10 skills:1 key:c4cf477894
## Problem 5.2: Counting

The `gf_counts()` function constructs a graphic with bars representing the counts in each category of a specified variable. For instance, the graphic shows the number of people in a clinical study of treatment for addition whose problem is linked to each of several drugs.

The count itself is not a variable, but is being derived from a categorical variable, in this case the variable `substance`. The formula given to `gf_counts` will have only a right-hand side: `~ substance`. This tells what variable to place on the x-axis. The count will be calculated and placed on the y-axis.

*** =instructions
- Attach the data table `CPS85` from the package `"mosaicData"`.
- Use `gf_counts()` to graph the number of people in `CPS85` who work in each `sector` of the economy.

*** =pre
```{r}
library(statisticalModeling)
data(HELPrct, package = "mosaicData")
gf_counts( ~ substance, data = HELPrct)
```

*** =sample_code
```{r}
library("statisticalModeling")
data(___, package = ___)

gf_counts( __one_sided_formula__, data = ___)
```

*** =solution
```{r}
library("statisticalModeling")
data(CPS85, package = "mosaicData")
gf_counts( ~ sector, data = CPS85)
```

*** =sct
```{r}
test_student_typed("\"mosaicData\"", not_typed_msg = "When using `data()`, be sure to give the name of the package in quotes.")
test_student_typed("mosaicData", not_typed_msg = 'Are you getting the `CPS85` data from eht `"mosaic"` package?')
test_student_typed("CPS85", not_typed_msg = "Remember, it's the `CPS85` data table that is to be used here.")
test_function("gf_counts")
success_msg("One to the next form of graph.")
```

*** =hint
Remember, the formula will be one-sided: `~ sector`.

--- type:NormalExercise lang:r xp:10 skills:1  key:8056051ae0
## Problem 5.3 Box-and-whisker plots

Box-and-whisker plots are a way to show how a quantitative variable (like `wage` in the `CPS85` data) depends on a categorical variable (like `sector`). Use the `gf_boxplot()` function to draw these. The formula will be of the form quantitative_var `~` categorical_var.

*** =instructions
- Use `gf_boxplot()` to make a box-and-whisker plot of `wage` versus `sector` in the `CPS85` data.

*** =pre
```{r}
#
```

*** =hint
Fill in the left blank (`___`) with the appropriate formula. The right blank should be filled in with the `data = ` argument, specifying, of course, the data table to use in making the plot.

*** =sample_code
```{r}
library("statisticalModeling")
data(CPS85, package = "mosaicData")

___(___, ___)
```

*** =solution
```{r}
library("statisticalModeling")
data(CPS85, package = "mosaicData")

gf_boxplot(wage ~ sector, data = CPS85)
```

*** =sct
```{r}
test_function("gf_boxplot")
success_msg("There are many other forms of plots in the `gf_` interface. They all work in basically the same way.")
```
