---
title       : "Data Computing: Chapter 4"
description : Exercises
---

--- type:MultipleChoiceExercise lang:r xp:10 skills:1  key:75fbbe31ff
## Problem 4.1

For this course, most data will come to you in data-table form. But there are several ways that the data might be provided:

* As data from an R package. Many R packages, including `ScientificProgramming`, provide data tables as part of the package. To access these tables, you can load the package. (In these DataCamp exercises, this has often been done for you.)
* As a file. Data-table files come in many different types. The type is often indicated by the last part of the name (the "filetype extension"). Three common types are:
    - a specialized spreadsheet file, e.g. `.xmlx` in the Excel system.
    - a generic spreadsheet file, often a `.csv` (comma-separated values).
    - a highly efficient format provided by R with file endings like `.rda` or `.Rdata`.

You refer to a table from a package by name, **not in quotes**. The name has to be a legal R object name. The name will **not** end with a filename extension such as `.csv` or `.Rda`.

You refer to a data file by a name also, **always in quotes**. The name often consists of many parts, separated by dashes. 

* Files available over the internet have names beginning with something like `http://` and end with extensions like `.csv` or `.Rdata`, etc.
* Files on your own computer (or on your account in the RStudio server) often start with `/` or `./` or `~/` and end with `.csv` or `.Rdata`, etc.


Which of the following is a data table identified by `"http://tiny.cc/dcf/CountryCodes.rda"`.


*** =instructions
- A file on my computer.
- A file available through the internet.
- A file provided by a package.

*** =hint
Look at the name of the file.

- Is it in quotes?
- Does it have foward slashes in it? 
- Does it start with something like `https::` or does it start with a single `/` or `~/` or `./`?
- Does it end with an extension like `.csv` or `.Rda`?

*** =sct
```{r}
msg1 <- "No. Notice how the name begins."
msg2 <- "Right. The name starts with a web indicator (`http:`) and ends with a filetype extension (`.rda`)."
msg3 <- "The name isn't in quotes, so it can't refer to a file."
test_mc(correct = 2, feedback_msgs = c(msg1, msg2, msg3))
```

--- type:NormalExercise lang:r xp:10 skills:1  key:cea17e0f68
## Problem 4.2

In the exercises and other activities for *Data Computing*, you will often see instructions like this:

> Use the `BabyNames` data table to ...

Note that the name is not in quotes, suggesting that it is a data table provided by a package. Unfortunately, you can't tell just from the name what package it is. If in doubt, one way to figure out which package provides the data table is with the `??` help notation, e.g.
```r
??BabyNames
```

It's also possible to refer to package data by explicitly naming the package, like this:

> Use the `DataComputing::BabyNames` data table to ...

The name before the double colons is the package name. The data table name follows the double colons. 

In order to use a data table from a package, you should either attach the package (with the `library()` command) or use the `data()` function. So either

    library(DataComputing)
    # ... or ...
    data(BabyNames, package = "DataComputing")


Either way, you will have access to the data table by name (e.g. `BabyNames`). It is not quoted, even though the name of the package is in quotes.

*** =Instructions
You've been referred to a data table `CPS85`, but don't know what package it comes from.

- Use `??` to get some help locating `CPS85`.
- Use the `data()` function to bring the data table into your session.

*** =sample_code
```{r}
??CPS85

data( .___, package = ".___")
```

*** =solution
```{r}
data(CPS85, package = "mosaicData")
```

*** =sct
```{r}
success_msg("Good.")
```
