---
title       : "Data Computing: Chapter 1"
description : Exercises
attachments :
  slides_link : https://s3.amazonaws.com/assets.datacamp.com/course/teach/slides_example.pdf
---

--- type:NormalExercise lang:r xp:50 skills:1 key:7edaec5a41
## Starting with R graphics

In your work with *Data Computing*, you will be using the `ggplot2` package for making graphics.  The sample code shows a few lines from a data table named `Diamonds`. The `ggplot()` command plots price against size (`carat`) for different cuts of diamonds.

*** =instructions
- Execute each of the two commands in the sample code to verify that it is working.
- Once you have done this, modify the `ggplot()` command so that the `clarity` variable is used instead of `cut`. If you read the existing command carefully, you should be able to figure out how to do this.

*** =hint
The phrase `color = cut` instructs `ggplot()` to set the color of each dot according to the value of the variable `cut`. So change `cut` to `clarity`.

*** =pre_exercise_code
```{r}
library(ggplot2)
```

*** =sample_code
```{r}
# Show the first few lines of the data table
head(diamonds)
# Plot out some of the data
ggplot(diamonds, aes(x = carat, y = price, color = cut)) + 
  geom_point()
# Modify the above to display the diamonds' clarity rather than cut.
```

*** =solution
```{r}
ggplot(diamonds, aes(x = carat, y = price, color = clarity)) + 
  geom_point()
```

*** =sct
```{r}
test_student_typed(c("color *= *clarity"), fixed = FALSE, 
              not_typed_msg = "Remember to set color = clarity."  )
success_msg("Good. Even though you may never have programmed before, you were still able to figure it out!")
```

--- type:NormalExercise lang:r xp:50 skills:1 key:8553b72780
## Starting with wrangling

The sample code finds the mean price for each cut of diamonds. Look through the code to see where each of those variables, `price` and `cut`, appears.

*** =instructions
- Modify the code to find the mean price for each clarity of diamonds. 


*** =hint
Notice that the variable `cut` appears in the `group_by()` part of the expression. You can change `cut` to `clarity` to get the job done.

*** =pre-exercise-code
```{r}
library(dplyr)
library(ggplot2)
```

*** =sample_code
```{r}
diamonds %>%
  group_by(cut) %>%
  summarise(val = mean(price))
```

*** = solution
```{r}
Diamonds %>%
  group_by(clarity) %>%
  summarise(val = mean(price))
```


*** =sct
```{r}
test_student_typed("group_by\\( *clarity *\\)", fixed = FALSE, 
                   not_typed_msg = "Have you changed the variable name in `group_by(cut)` to `clarity`?")
success_msg("Good. The purpose of this exercise was just to give you practice with DataCamp.")
```