---
title: "DC-2017-01-01-d386f"
output: html_document
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

An R package is a way to distribute software and data. The examples in the *Data Computing* book are often based on data provided by the `DataComputing` package, written specifically to go along with the book. But in your work you will also encounter examples that use data from other packages, such as `mosaicData`.

In the text of an exercise you will often see instructions like this: 

> Use the `NCHS` data table to ...

or, like this:

> Use the `DataComputing::HappinessIndex` data table to ...

In both cases, the name refers to a data table provided by a package. The longer name, `DataComputing::HappinessIndex` contains both the name of the package (`DataComputing`) and the name of the data table itself (`HappinessIndex`). The double colons are a form of punctuation to separate the package name from the data table name.

In the shorter example, the data table is named `NCHS`. But which package does it come from?

To find out, you can use a command like that shown in the code pane.

```{r DC-2017-01-01-d386f-scratch, exercise = TRUE, echo = FALSE}
??NCHS
```

```{r DC-2017-01-01-d386f-scratch-hint, echo = FALSE}
Try the command `??CoolingWater`
```

Run the command. The output will contain the double-colon form of the table name, from which you can figure out the name of the package providing `NCHS`.



```{r DC-2017-01-01-d386f, echo = FALSE}
question('Use the code pane above to figure out what package provides the table named `CoolingWater`.',
  answer("`mosaicData`", 
         correct = TRUE,
         message = "Right. `mosaicData` is a package widely used in teaching statistics." ),
  answer("`DataComputing`", 
         correct = FALSE, 
         message = "Sorry. Many of the examples used in \"Data Computing\" will draw on the data in the `DataComputing` package, but not this one."),
  answer("`ggplot2`", 
         correct = FALSE,
         message = "Did you see `ggplot2::GaltonData` in the output? I don't think so."),
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```




