---
title: "DC-2017-01-01-fc26d"
output: html_document
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

```{r DC-2017-01-01-fc26d-setup, echo = FALSE}
# code to be evaluated before exercise code
library(mosaicData)
library(DataComputing)
```

Here's one way to access a data table provided by a package:

```{r}
data(BabyNames, package = "DataComputing")
```
    
The `data()` function takes two arguments. The first is the name of the data table that you want to access. Note that it is *not* in quotes. The second is a "named argument." The name of the argument is `package`. The `=` in the above example says to set the value of the argument called `package` to the string constant `"DataComputing"`. Note that the package name is in quotes.

The result of a command like the above is to create a new object in R that you can refer to by name. For instance, you can see the names of the variables with the `names()` function:

```{r}
names(BabyNames)
```

**Your task**: Access the `CPS85` data table. Here's a code pane you can use to figure out what package `CPS85` comes from.

```{r DC-2017-01-01-fc26d-scratch, exercise = TRUE}

```

```{r DC-2017-01-01-fc26d-scratch-hint}
??CPS85
```

Once you know the name of the package that provides `CPS85`, you can fill in the blanks in the code pane below in order to access the data table and look at the first few rows of it.


```{r DC-2017-01-01-fc26d, exercise = TRUE, exercise.setup = "DC-2017-01-01-fc26d-setup", exercise.eval = FALSE}
data(_____, _____)
head(_____)
```

<!-- narrative to wrap up (if any) goes here -->

```{r DC-2017-01-01-fc26d-hint-1, echo = FALSE}
# The CPS85 data table comes from the "mosaicData" package.
# Remember the quotes when referring to "mosaicData"
```

```{r DC-2017-01-01-fc26d-hint-2, echo = FALSE}
head(CPS85)
```

```{r DC-2017-01-01-fc26d-solution, echo = FALSE}
data(CPS85, package = "mosaicData")
head(CPS85)
```

```{r DC-2017-01-01-fc26d-check, echo = FALSE}
test_0 <- find_call("data(CPS85, whatever)", "the first argument to `data()` is the data table, e.g. `CPS85`")
test_1 <- find_call("data(whatever, package = whatever)", "the second argument to `data()` is `package =`")

test_2 <- find_names(data(CPS85), "remember to use the data() function to access CPS85.")
test_3 <- check_argument("data(CPS85, package = grab_this)", 
                         test = agrees(is.character(x), 
                                       "the name of the package should be in quotes."))
test_4 <- find_constants("mosaicData", message = "the package containing the data is \"mosaicData\"")
test_5 <- find_call("data(whatever, package = 'mosaicData')", message = "argument should be the name of the package (in quotes).")
test_6 <- find_call("head(CPS85)", "give the data table as the argument to `head()`")

USER_CODE %>% test_0 %>% test_1 %>% test_2 %>% test_3 %>%  test_4 %>% test_5 %>% test_6
```


