---
title: "DC-2017-01-08-2f4d3"
output: html_document
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

```{r DC-2017-01-08-2f4d3-setup, echo = FALSE}
# code to be evaluated before exercise code
data(CPS85, package = "mosaicData")
library(statisticalModeling)
```

Box-and-whisker plots are a way to show how a quantitative variable (like `wage` in the `CPS85` data) depends on a categorical variable (like `sector`). Use the `gf_boxplot()` function to draw these. The formula will be of the form quantitative_var `~` categorical_var.

Use `gf_boxplot()` to construct this box-and-whisker plot using the `CPS85` data.

```{r 2f4d3, echo = FALSE}
library(statisticalModeling)
library(ggplot2)
data(CPS85, package = "mosaicData")
gf_boxplot(wage ~ sector, data = CPS85)
```


```{r DC-2017-01-08-2f4d3, exercise = TRUE, exercise.setup = "DC-2017-01-08-2f4d3-setup", exercise.eval = FALSE}
library("statisticalModeling")
data(CPS85, package = "mosaicData")

___(___, ___)
```

<!-- narrative to wrap up (if any) goes here -->

<div id = "DC-2017-01-08-2f4d3-hint">
Fill in the left blank (`___`) with the appropriate formula. The right blank should be filled in with the `data = ` argument, specifying, of course, the data table to use in making the plot.
</div>

```{r DC-2017-01-08-2f4d3-solution, echo = FALSE}
library("statisticalModeling")
data(CPS85, package = "mosaicData")

gf_boxplot(wage ~ sector, data = CPS85)
```

```{r DC-2017-01-08-2f4d3-code-check, echo = FALSE}
# put pre-evaluation checking here. This can be blank, in which case
# the code will be checked by the interpreter with the usual R error messages
# shown in the even of a problem.
check_blanks(USER_CODE)
```

```{r DC-2017-01-08-2f4d3-check, echo = FALSE}
set_success_message("Good job!") # change as you like
test_1 <- find_call("gf_boxplot()",
                    message = "use `gf_boxplot() to make the plot.")
test_2 <- find_call("gf_boxplot(whatever, data = CPS85)",
                    message = "use the `CPS85` data table as the `data` argument to `gf_boxplot().")
test_3 <- check_argument("gf_boxplot(grab_this, whatever)",
                         test = match_formula(wage ~ sector))
USER_CODE %>% test_1 %>% test_2 %>% test_3
```


