---
title: "DC-2017-01-08-b769a"
output: html_document
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
library(DataComputing)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

```{r DC-2017-01-08-b769a-setup, echo = FALSE}
library(DataComputing)
```
A data verb is a function that takes a data table as input and produces a data table as output. `sample_n()` is a data verb that performs a very simple tasks: it draws a random sample of cases from the input data table and presents that sample as the output.

The code pane shows a simple data-wrangling expression using `sample_n()`. Run that expression several times to see that the output differs from run to run: the sample is random! The `size =` argument to `sample_n()` sets how big the sample will be.


- First, re-write the expression using pipe notation.
- Second, arrange that the output of the expression is stored in an object named `My_sample`.
- Finally, arrange the argument to `sample_n()` so that there are 10 cases in the output.


```{r DC-2017-01-08-b769a, exercise = TRUE, exercise.setup = "DC-2017-01-08-b769a-setup", exercise.eval = FALSE}
# read in the Births78 data table
data(Births78, package = "mosaicData")

# select a random sample of 3 cases
sample_n(Births78, size = 3)

# First, re-write the sample_n() above to use pipe notation


# Second, re-write the above to store the output under the name My_sample


# Last, arrange for there to be 10 random cases in My_sample

```

<!-- narrative to wrap up (if any) goes here -->

<div id="DC-2017-01-08-b769a-hint">
Two things change in pipe notation:

- The original expression began with a data verb whose first argument was a data table. The pipe expression begins with the input data table followed by a pipe symbol `%>%`.
- In the pipe expression, the data verb comes after the pipe.
- In the pipe expression, the data table is **not** given as an argument inside the parentheses. Instead, the pipe is telling the data verb which data table to take as input.
</div>

```{r DC-2017-01-08-b769a-solution, echo = FALSE}
# First
Births78 %>% 
  sample_n(size = 3)
# Second
My_sample <- 
  Births78 %>%
  sample_n(size = 3)
# Last
My_sample <- 
  Births78 %>%
  sample_n(size = 10)
```

```{r DC-2017-01-08-b769a-code-check, echo = FALSE}
# put pre-evaluation checking here. This can be blank, in which case
# the code will be checked by the interpreter with the usual R error messages
# shown in the even of a problem.
check_blanks(USER_CODE)
```

```{r DC-2017-01-08-b769a-check, echo = FALSE}
set_success_message("Good job!") # change as you like
test_1 <- find_pipe_start("Births78",
                          message = "you should use `Births78` as the start of a pipe into `sample_n()`.")
test_2 <- find_call("sample_n(whatever, size = 3)", 
                    message = "pipe `Births78` into `sample_n(), giving sample_n() the argument `size = 3`.")
test_2a <- find_call("sample_n(whatever, Births78, whatever)")
test_3 <- find_assignment("My_sample", "did you do an assignment to `My_sample`?")
test_4 <- check_value(test = agrees(nrow(x) == 10), 
                      message = "in the last step, the sample size should be 10.")
USER_CODE %>% test_1 %>% then(inclusive = TRUE) %>% 
  test_2a %>% 
  was_mistake(message = "when piping into a function, the data table does not need to be given explicitly to the function.") %>% 
  test_2 %>% test_3 %>% final_ %>% test_4 
```


