---
title: "DC-2017-01-08-63712"
output: html_document
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

```{r DC-2017-01-08-63712-setup, echo = FALSE}
library(DataComputing)
data(Births78, package = "mosaicData")
```

One of the most widely used data verbs is `summarise()`. Like all data verbs, `summarise()` takes as input a data table. It performs a reduction on the data table, for example calculating the sum of the values in a variable.

Of course, you have to tell `summarise()` what summaries you want to perform. All summaries involve a "reduction verb", a function like `mean()` or `sum()` that takes the values in a variable and reduces them to a single value.

We'll use the `Births78` data in this exercise. This data table gives the number of births in the US on each day of the year in 1978. The variable `births` gives the number of babies born on each day.

- You will use the data verb `summarise()` and will pipe the `Births78` data table to be the input to `summarise()`. You will also give, as an argument to `summarise()` an expression that calculates the total `sum()` of `births` 
- Give the argument the name `total` so that the output data table has a variable named `total`.


```{r DC-2017-01-08-63712, exercise = TRUE, exercise.setup = "DC-2017-01-08-63712-setup", exercise.eval = FALSE}
# provide access to Births78
data(Births78, package = "mosaicData")
# the data wrangling package
library("dplyr")

Births78 %>% summarise(___)
```

<!-- narrative to wrap up (if any) goes here -->

<div id="DC-2017-01-08-63712-hint">
The reduction verb `sum()` takes a variable as input and provides as output the sum of all the values in that variable. `sum(births)` is an expression that can be given as an argument to the data verb `summarise()` to instruct it to evaluate the expression on the data table piped in as input. Naming the argument, e.g. `summarise(total = sum(births))` gives the name `total` to the corresponding output of `summarise()`.
</div>

```{r DC-2017-01-08-63712-solution, echo = FALSE}
data(Births78, package = "mosaicData")
library("dplyr") # or "DataComputing"

Births78 %>% summarise(total = sum(births))
```

```{r DC-2017-01-08-63712-code-check, echo = FALSE}
# put pre-evaluation checking here. This can be blank, in which case
# the code will be checked by the interpreter with the usual R error messages
# shown in the even of a problem.
check_blanks(USER_CODE)
```

```{r DC-2017-01-08-63712-check, echo = FALSE}
set_success_message("Good job!") # change as you like
test_1 <- find_call("sum(births)", 
                    message = "in summarise(), use `sum()` on the `births` variable to get the total number of births.")

test_2 <- check_value(test = agrees("total" %in% names(x)),
                      message = "use `total` as the name of the variable holding `sum(births)") # replace with your own
USER_CODE %>% test_1 %>% final_ %>% test_2
```


