---
title: "DC-2017-01-08-7d4bc"
output: html_document
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

```{r DC-2017-01-08-7d4bc-setup, echo = FALSE}
# code to be evaluated before exercise code
```

Wrangling often involves computing summaries for different groups of cases. The `group_by()` data verb allows you to specify how to divide the cases into groups so that `summarise()` and other data verbs know what to do. 

Typically, you will define groups based on the level of one or more a variables. For instance, the `wday` variable in `Births78` tells which day of the week --- Sunday, Monday, ... --- each of the dates corresponds to.

- Pipe `Births78` into `group_by()`. Give `group_by()` the argument `wday`, so that groups are defined by the day of the week.
- The output of `group_by()` should be piped into `summarise()`. Arrange `summarise()` to have an argument named `total` that sums the number of `births`.
- The result should be a separate sum, named `total`, for each day of the week.

```{r DC-2017-01-08-7d4bc, exercise = TRUE, exercise.setup = "DC-2017-01-08-7d4bc-setup", exercise.eval = FALSE}
data(Births78, package = "mosaicData")
library("dplyr")
Births78 %>%
  group_by(___) %>%
  summarise(___ = sum(___))
```

<!-- narrative to wrap up (if any) goes here -->

<div id ="DC-2017-01-08-7d4bc-hint">
Pipe `Births78` into `group_by(wday)`. Then, pipe the output of `group_by(wday)` to a `summarise()` function whose argument computes the quantity `total = sum(births)`. 
</div>

```{r DC-2017-01-08-7d4bc-solution, echo = FALSE}
data(Births78, package = "mosaicData")
library("dplyr")
Births78 %>%
  group_by(wday) %>%
  summarise(total = sum(births))
```

```{r DC-2017-01-08-7d4bc-code-check, echo = FALSE}
# put pre-evaluation checking here. This can be blank, in which case
# the code will be checked by the interpreter with the usual R error messages
# shown in the even of a problem.
check_blanks(USER_CODE)
```

```{r DC-2017-01-08-7d4bc-check, echo = FALSE}
set_success_message("Good job. Note that the output contains *only* the variables used for grouping and the variables created by `summarise()`.") # change as you like
test_1 <- find_call("group_by(whatever, wday)", 
                    message = "use `wday` as the grouping variable, that is, as an argument to `group_by()`.")
test_2 <- find_call("sum(births)", 
                    message = "use `sum()` within summarise to add up the `births`.")
test_3 <- check_value(test = agrees("total" %in% names(x)), 
                      message = "the output variable containing the sum of births should be called `total`.")
test_4 <- find_call("summarise()", "`summarise()` should follow `group_by()`.")
USER_CODE %>% test_1 %>% test_2 %>% test_3
USER_CODE %>% test_1 %>% then %>% test_4
```



```{r DC-2017-01-08-7d4bc-follow-up, echo = FALSE}
question("Based on your results above, which days of the week are the *least* number of babies born?",
  answer("Weekdays", correct = FALSE, message = "We're looking for the days with the *least* number of babies."),
  answer("Weekends", correct = TRUE),
  answer("Mondays and Fridays", correct = FALSE), 
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```

