---
title: "DC-2017-01-09-81756"
output: html_document
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
library(DataComputing)
```

```{r DC-2017-01-09-81756-setup, echo = FALSE}
data(CountryData, package = "DataComputing")
library("ggplot2")
library("dplyr")
```

In previous exercises, you used a formula-based interface to the `ggplot2` system for graphics. That formula-based interface is intended to be easy for getting started with making simple graphics. In these exercises, you'll practice with the `ggplot` interface itself.

The `ggplot()` function is used to define a the graphics frame. The frame it makes is blank, ready to have additional layers of glyphs added to it. The typical arguments to `ggplot()` are:

1. A data table, given as the first argument or piped into `ggplot()`.
2. An `aes()` statement which constructs the mapping from variables in the data table to the `x` and `y` aesthetics, that is, the frame itself.

The graphic shows a (blank) frame constructed by `ggplot()`. (We'll add layers to this blank frame in the exercises that follow.)

```{r echo = FALSE, out.width = "50%"}
CountryData %>% 
  ggplot(aes(x = life, y = death))
```

- Read from the graph the variables that have been mapped to the x and y aethetics.
- Fill in the blanks in order to construct a command that will reproduce the blank frame.


```{r DC-2017-01-09-81756, exercise = TRUE, exercise.setup = "DC-2017-01-09-81756-setup", exercise.eval = FALSE}
# Provide access to CountryData
data(CountryData, package = "DataComputing")

# Attach the ggplot2 package
library("ggplot2")

# Fill in the blanks ...
CountryData %>%
  ggplot(aes(x = ___, y = ___))
```

<!-- narrative to wrap up (if any) goes here -->

<div id='DC-2017-01-09-81756-hint'>
As you can see, `life` is being mapped to the x aesthetic, `death` to the y aesthetic. It will seem a bit odd at first, but remember to use `aes()` as a function, given as an argument to `ggplot()`, and map the aesthetics by giving appropriate arguments to `aes()`.
</div>

```{r DC-2017-01-09-81756-solution, echo = FALSE}
data(CountryData, package = "DataComputing")
library("ggplot2")
CountryData %>% ggplot(aes(x = life, y = death))
```

```{r DC-2017-01-09-81756-code-check, echo = FALSE}
# put pre-evaluation checking here. This can be blank, in which case
# the code will be checked by the interpreter with the usual R error messages
# shown in the even of a problem.
check_blanks(USER_CODE)
```

```{r DC-2017-01-09-81756-check, echo = FALSE}
set_success_message("Good job!") # change as you like
test_1 <- find_call("aes(x = life, y = whatever)",
                    message = "map `life` to the x axis.")
test_2 <- find_call("aes(x = whatever, y = death)",
                    message = "map `death to the y axis")
USER_CODE %>% test_1 %>% test_2
```


