---
title: "DC-2017-01-09-75a09"
output: html_document
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
library(DataComputing)
```

```{r DC-2017-01-09-75a09-scratch-setup, echo = FALSE, message = FALSE}
# code to be evaluated before exercise code
library(statisticalModeling)
library(DataComputing)
```

You've already seen how `gf_point()` can be used to draw graphics. For example, the scratch chunk below already contains the commands to draw a scatterplot that relates `death` rates, `life` expectancy, and Gross Domestic Project per capita (`GDPcapita`, which is a measure of economic activity). 

```{r DC-2017-01-09-75a09-scratch, exercise = TRUE, exercise.eval = FALSE, warning = FALSE, message = FALSE, out.width = "50%"}
library(statisticalModeling)

gf_point(death ~ life + alpha:GDPcapita, data = CountryData)
```

Functions like `gf_point()` are built on another graphics system that is very widely used in Data Science, `ggplot2`. Many people find the formula interface provided by `gf_point()` easier to use than the native `ggplot2` interface, but once you get used to `ggplot2` it is just as easy and it provides greater flexibility.

By using and argument `verbose = TRUE` to `gf_point()`, you can see exactly what is the `ggplot2` command created.

Try that in the above code chunk.

Now copy and paste that `ggplot2()` command into the following chunk, and confirm that it makes exactly the same plot.

```{r DC-2017-01-09-75a09-setup, warning = FALSE, message = FALSE, out.width = "50%", echo = FALSE}
library(statisticalModeling)
data(CountryData, package = "DataComputing")
```

```{r DC-2017-01-09-75a09, exercise = TRUE, exercise.setup = "DC-2017-01-09-75a09-setup", exercise.eval = FALSE, warning = FALSE, message = FALSE, out.width = "50%"}

```

<!-- narrative to wrap up (if any) goes here -->

<div id="DC-2017-01-09-75a09-hint">
Add `verbose = TRUE` as an argument to `gf_point()` in order to see what the corresponding `ggplot2` command looks like.
</div>

```{r DC-2017-01-09-75a09-solution, echo = FALSE}
# code or text that's a solution to the exercise
```

```{r DC-2017-01-09-75a09-code-check, echo = FALSE}
# put pre-evaluation checking here. This can be blank, in which case
# the code will be checked by the interpreter with the usual R error messages
# shown in the even of a problem.
check_blanks(USER_CODE)
```

```{r DC-2017-01-09-75a09-check, echo = FALSE}
set_success_message("Good.") # change as you like
test_1 <- find_call("ggplot()", 
                    message = "use the `ggplot2` command in this code pane.") 
test_2 <- find_call("geom_point()", 
                    message = "did you include the whole `ggplot2` command, including `+ geom_point()`?")
test_3 <- check_value(test = agrees(inherits(x, "ggplot")),
                      message = "it doesn't look like you copied the whole command.")
USER_CODE %>% test_1 %>% test_2 %>% final_ %>% test_3
```


