---
title: "DC-2017-01-09-b82d9"
output: html_document
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

```{r DC-2017-01-09-b82d9-setup, echo = FALSE}
library(DataComputing)
```

A blank frame is useful only as a place to draw glyphs.  The `ggplot()` function only creates the frame, it doesn't do any drawing.

You draw glyphs by adding a layer to the plot. There are many, many functions in the `ggplot` system for drawing different types of glyphs. For example a scatter plot can be made with `geom_point()`, a box-and-whiskers plot with `geom_boxplot()`, and so on.

It's typical that the x and y aesthetics are set in the `aes()` function, contained as an argument to `ggplot()`. Similarly, the data table containing the cases to be plotted is piped into the `ggplot()` function. This is the way that the command in the folloing code pane is set up.

To add a layer into the frame, follow the `ggplot()` function call with a `+` and follow that with a call to the layer-drawing function. (The `+` is a kind of piping operator, specifically for `ggplot()`. In data wrangling, the pipe operator is, of course, `%>%`. It's only for historical reasons that `ggplot()` uses `+` instead of `%>%`.)

* Add a scatter-plot layer to the plot being made in the code pane.

```{r DC-2017-01-09-b82d9, exercise = TRUE, exercise.setup = "DC-2017-01-09-b82d9-setup", exercise.eval = FALSE, warning =FALSE, message=FALSE, out.width="50%"}
CountryData %>%
  ggplot(aes(x = life, y = death))
```

<!-- narrative to wrap up (if any) goes here -->

<div id='DC-2017-01-09-b82d9-hint'>
Scatter plots are made with `geom_point()`
</div>

```{r DC-2017-01-09-b82d9-solution, echo = FALSE}
CountryData %>%
  ggplot(aes(x = life, y = death)) +
  geom_point()
```

```{r DC-2017-01-09-b82d9-code-check, echo = FALSE}
# put pre-evaluation checking here. This can be blank, in which case
# the code will be checked by the interpreter with the usual R error messages
# shown in the even of a problem.
check_blanks(USER_CODE)
```

```{r DC-2017-01-09-b82d9-check, echo = FALSE}
set_success_message("Good job!") # change as you like
test_1 <- find_call("whatever + whatever",
                    message = "use `+` to connect the frame and the glyph layer.")
test_2 <- find_call("geom_point()", "the added layer should be a scatter plot of the cases in `CountryData`.")
test_3 <- check_value(test = agrees(inherits(x, "ggplot")), 
                      message = "it doesn't look like the plot was made.")
USER_CODE %>% test_2 %>% test_1 %>% test_2 %>% test_3
```


