---
title: "Data Computing: Chapter 1"
output: 
  tutor::tutorial: default
  html_document: 
    number_sections: yes
    toc: yes
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```


<!-- even though this chunk is empty, it sets up authentication for data logging -->

<!--
```{r child = checkr::authentication()}
```
-->


# Introduction to tutorial exercises

```{r child="Chapter-01/DC-01-intro.Rmd"}
```

## ... and questions

```{r child="Chapter-01/DC-2016-12-22-f379e.Rmd"}
```

# Warm-up Exercises

You're just at the start of the course, so you can hardly be expected to be able to write complete data-wrangling and visualization commands. In these warm-up exercises, you're asked to read some commands and make some very small modifications to them. Later tutorials will provide a systematic introduction. 


## Warm-up 1: Reading code

```{r child = "Chapter-01/DC-2016-12-22-50dc3.Rmd"}
```

## Warm-up 2: Wrangling sequences

```{r child = "Chapter-01/DC-2016-12-22-57e2d.Rmd"}
```

## Warm-up 3: Graphics

```{r child = "Chapter-01/DC-2016-12-30-a163b.Rmd"}
```

## Warm-up 4: Diamonds

```{r child = "Chapter-01/DC-2016-12-30-03b65.Rmd"}
```
