---
title: "DC-2017-01-08-32f7b"
output: html_document
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
library(DataComputing)
library(statisticalModeling)
data(CPS85, package = "mosaicData")
```

```{r DC-2017-01-08-32f7b-setup, echo = FALSE}
data(CPS85, package = "mosaicData")
library(ggplot2)
library(DataComputing)
library(statisticalModeling)
```

In the previous chapter, you graphed a summary of the `CPS85` data like that shown in the figure: counts of people working in each sector of the economy. 

```{r}
gf_counts(~ sector, data = CPS85)
```

In this exercise, you're going to add new aethetics to the bars and facet the graph. Things have been set up so that you need only replace the blanks `___` with the appropriate variable. 

- Set the "fill" color for the bars based on whether the person belongs to a `union`. To do this, fill in the blank following `fill:` with the variable that is to be mapped to the fill aesthetic.
- Facet the graph based on `sex`. To do this, complete the formula argument to the `facet_grid()` function.


```{r DC-2017-01-08-32f7b, exercise = TRUE, exercise.setup = "DC-2017-01-08-32f7b-setup", exercise.eval = FALSE}
library("statisticalModeling")
library("ggplot2")
data(CPS85, package = "mosaicData")
gf_counts( ~ sector + fill:___, data = CPS85) + facet_grid( ~ ___)
```

<!-- narrative to wrap up (if any) goes here -->

<div id = "DC-2017-01-08-32f7b-hint">
Put the right variable names in the blanks.
</div>

```{r DC-2017-01-08-32f7b-solution, echo = FALSE}
library(statisticalModeling)
library(ggplot2)
data(CPS85, package = "mosaicData")
gf_counts( ~ sector + fill:union, data = CPS85) + facet_grid( ~ sex)
```

```{r DC-2017-01-08-32f7b-code-check, echo = FALSE}
# put pre-evaluation checking here. This can be blank, in which case
# the code will be checked by the interpreter with the usual R error messages
# shown in the even of a problem.
check_blanks(USER_CODE)
```

```{r DC-2017-01-08-32f7b-check, echo = FALSE}
set_success_message("Good job!") # change as you like
test_1 <- find_call("gf_counts()")
test_2 <- check_argument("gf_counts(grab_this, whatever)",
                         test = match_formula(~ sector + fill:union),
                         message = "set the fill aesthetic using `union`.")
test_3 <- find_call("facet_grid()", "remember to facet the graph")
test_4 <- check_argument("facet_grid(grab_this)",
                         test = match_formula(~ sex),
                         message = "facet the graph by `sex`")
USER_CODE %>% test_1 %>% test_2 %>% test_3 %>% test_4 
```

<a href="#" title = "DC-2017-01-08-32f7b">+</a>
