---
title: "Data Computing: Chapter 7"
author: "Daniel Kaplan"
output: html_document
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(tutor)
library(ggplot2)
library(dplyr)
library(checkr)
library(statisticalModeling)
library(DataComputing)
library(mosaicData)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

## Problem 7.1: Pipes and data verbs

A data verb is a function that takes a data table as input and produces a data table as output. `sample_n()` is a data verb that performs a very simple tasks: it draws a random sample of cases from the input data table and presents that sample as the output.

The sample code shows a simple data-wrangling expression using `sample_n()`. Run that expression several times to see that the output differs from run to run: the sample is random! The `size =` argument to `sample_n()` sets how big the sample will be.

Now you are going to translate the `sample_n()` statement into pipe notation. Following each of the First/Second/Last comments,
add your command to implement the expression as a pipe.

- First, re-write the expression using pipe notation.
- Second, arrange that the output of the expression is stored in an object named `My_sample`.
- Last, arrange the argument to `sample_n()` so that there are 10 cases in the output.


```{r DC-seven-1, exercise = TRUE}
# read in the Births78 data table
data(Births78, package = "mosaicData")

# select a random sample of 3 cases
sample_n(Births78, size = 3)

# First, re-write the above to use pipe notation


# Second, re-write the above to save the output in My_sample


# Last, arrange for there to be 10 random cases in My_sample

```

```{r DC-seven-1-solution, echo = FALSE}
library("dplyr")
# read in the Births78 data table
data(Births78, package = "mosaicData")

# select a random sample of 3 cases
sample_n(Births78, size = 3)

# First, re-write the above to use pipe notation
Births78 %>% sample_n(size = 3)

# Second, re-write the above to save the output in My_sample
My_sample <- Births78 %>% sample_n(size = 3)

# Last, arrange for there to be 10 random cases in My_sample
My_sample <- Births78 %>% sample_n(size = 10)
```

```{r DC-seven-1-check, echo = FALSE}
test_0 <- find_assignment("..tmp1..", "start with the pipe operator 'Births78 %>%'")
test_1 <- find_call("sample_n(..tmp1.., size = whatever)", "follow the pipe with sample_n()")
test_2 <- find_constants(3, match_number(3, "start step 1 with a sample size of 3."))
test_4 <- find_assignment("My_sample", "in step 2, assign the name 'My_sample' to your result.")
test_5 <- find_constants(3, message = "in the second step, the sample size should be 3.")
test_6 <- find_constants(10, message = "in the third step, the sample size should be 10.")
test_7 <- check_value(test = function(x) ifelse(nrow(x) == 10, "", sprintf("sample size of 10, not %s!", nrow(x))))
USER_CODE %>% test_0 %>% test_1 %>% test_2 
USER_CODE %>% test_4 %>% test_5 %>% then %>% test_4 %>% test_6 %>% final_ %>% test_7
```


```{r, echo = FALSE, eval = FALSE}
test_student_typed("size *= *10", fixed = FALSE,
                   not_typed_msg = "Did you change the sample size to 10?")
test_student_typed("Births78 *%>% *sample_n", fixed = FALSE,
                   not_typed_msg = "Remember, it's `data_table %>% data_verb`.")
test_student_typed("My_sample *(=|<-)", fixed = FALSE,
                   not_typed_msg = "Did you assign the output to `My_sample`?")
```


## Problem 7.2: The summarise() data verb

One of the most widely used data verbs is `summarise()`. Like all data verbs, `summarise()` takes as input a data table. It performs a reduction on the data table, for example calculating the sum of the values in a variable.

Of course, you have to tell `summarise()` what summaries you want to perform. All summaries involve a "reduction verb", a function like `mean()` or `sum()` that takes the values in a variable and reduces them to a single value.

We'll use the `Births78` data in this exercise. This data table gives the number of births in the US on each day of the year in 1978. The variable `births` gives the number of babies born on each day.

Construct a wrangling statement that uses `summarise()` and `sum()` to find the total number of births. The result of the calculation should be a data table with a single column named `total` and just one row containing the total number of births.

1. Pipe the `Births78` data table to be the input to `summarise()`. 
2. The argument to `summarise()` will be named `total` and should be set equal to the sum of the values in the `birth` variable.

```{r DC-seven-2, exercise = TRUE}
data(Births78, package = "mosaicData")
library("dplyr")

Births78 %>% summarise(____)

```{r DC-seven-2-solution, echo = FALSE}
data(Births78, package = "mosaicData")
library("dplyr")

Births78 %>% summarise(total = sum(births))
```

```{r DC-seven-2-hint, echo = FALSE}
# The reduction verb `sum()` takes a variable as input and provides 
# as output the sum of all the values in that variable. `sum(births)` 
# is an expression that can be given as an argument to the data verb `summarise()` 
# to instruct it to evaluate the expression on the data table piped in as input. 
# Naming the argument, e.g. `summarise(total = sum(births))` gives the name `total` 
# to the corresponding output of `summarise()`.
```

```{r DC-seven-2-check, eval = FALSE}
test_0 <- find_pipe_start("Births78", "pipe `Births78` into summarise()") 
test_1 <- find_call("summarise()", "use the `summarise()` data verb.")
test_2 <- find_call("sum(births)", "use `sum()` in the argument to `summarise()`")
test_3 <- check_value(test = function(x) ifelse( names(x) == "total", "", "name the output variable 'total'."))
test_4 <- check_value(test = function(x) ifelse( nrow(x) == 1, "", "output should have just 1 row."))
USER_CODE %>% test_0 %>% test_1 %>% test_2 %>% test_3 %>% test_4
```

## Problem 7.3: Groupwise summaries

Wrangling often involves computing summaries for different groups of cases. The `group_by()` data verb allows you to specify how to divide the cases into groups so that `summarise()` and other data verbs know what to do. 

Typically, you will define groups based on the level of one or more a variables. For instance, the `wday` variable in `Births78` tells which day of the week --- Sunday, Monday, ... --- each of the dates corresponds to.

Earlier, you constructed a statement to find the total count of births:
```r
Births78 %>% summarise(total = sum(births))
```
In this exercise you'll modify that statement to find the total number of births on each day of the week. 

- Pipe `Births78` into `group_by()`. Give `group_by()` the argument `wday`, so that groups are defined by the day of the week.
- The output of `group_by()` should be piped into `summarise()`. Arrange `summarise()` to have an argument named `total` that sums the number of `births`.
- The result should be a separate sum, named `total`, for each day of the week.

```{r DC-setup, echo = FALSE}
library(DataComputing)
```


```{r DC-seven-3, exercise = TRUE, exercise.setup = 'DC-setup'}
data(Births78, package = "mosaicData")

Births78 %>%
  group_by(___) %>%
  summarise(___ = sum(___))
```

```{r DC-seven-3-solution, echo = FALSE}
data(Births78, package = "mosaicData")
library("dplyr")
Births78 %>%
  group_by(wday) %>%
  summarise(total = sum(births))
```


```{r DC-seven-3-check, echo = FALSE}
test_1 <- find_pipe_start("Births78", message = "use the Births78 data table from the mosaicData package")
test_2 <- find_constants("wday")
test_3 <- find_names(group_by(wday), message = "the argument to group_by() is the name of the variable you wnt to use to define the groups. In this case, it's wday. No quotes are needed. ")
test_4 <- check_value(test = agrees(all(c("wday", "total") %in% names(x))))
USER_CODE %>% test_1 %>% test_2 %>% 
  was_mistake(message = "variable names in dplyr data verbs should not be quoted.") %>%
  test_3 %>% final_ %>% test_4
```


## Problem 7.4: group_by() with other data verbs

The `group_by()` function simply marks the data table as having groups (specified by the arguments to `group_by()`). Those groups can be used by any data verb, not just `summarise()`.

In this exercise, you're going to pipe the output of `group_by()` into `sample_n()`. Examine the output and tried to figure out how `sample_n()` used the groups marked by `group_by()`.

```{r DC-seven-4b, exercise = TRUE, exercise.setup = 'DC-setup'}
data(Births78, package = "mosaicData")
# run this code
Births78 %>% 
  group_by(wday) %>%
  sample_n(size = 2)
```

```{r DC-seven-4, echo=FALSE}
question('Which way did sample_n() use the groups?',
  answer("It randomly picked a group and selected only cases within that group.", 
         message = "If this were right, all of the cases in the output would have the same value of wday."),
  answer("It operated separately on each group and collected the results for all the groups together into the output.", correct = TRUE),
  answer("It ignored the groups", message = "If it ignored the groups, there would be no pattern in the output relating to the groups. But there is. Look again."),
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```

## Problem 7.5: Not a data verb.

A data verb is a function that takes a data table as an input and produces a data table as an input.

In the console, try each of these R expressions on the `Births78` data table.

```{r DC-seven-5b, exercise = TRUE}
nrow(Births78)
names(Births78)
class(Births78)
```

```{r DC-seven-5b-hint, echo = FALSE}
When a data table is printed, the cases are numbered in sequence on the left, one per row, and the variable names appear across the top. In contrast, a simple "set" is just a series of numbers or character strings and can be printed with more than one item on a line.
```

```{r DC-seven-5, echo = FALSE}
question("Why aren't any of these data verbs?",
         answer("They don't take a data table as in input.",
                message = 'But they are taking `Births78` as input, and `Births78` is a data table.'),
         answer("They don't have any output.",
                message = "Each of them has an output."),
         answer('The output is not in the form of a data table. `nrow()` produces a single number, `names()` produces a set of character strings, and class() gives a character string identifying the class of the input.', correct = TRUE),
         allow_retry = TRUE,
         random_answer_order = TRUE)
```

## Problem 7.6: group_by()

`group_by()` can use multiple variables when forming groups. You do this by giving multiple arguments to `group_by()`; each argument is a variable in the data table input.

Figure out and explain what groups are formed by `group_by()` in this data-wrangling statement.

```{r DC-seven-6-b, exercise = TRUE}
CPS85 %>%
  group_by(sex, sector) %>%
  summarise(wage = mean(wage))
```    

```{r DC-seven-6, echo = FALSE}
question("What is group_by() accomplishing in the above statement?",
         answer("It divides the groups identified by sex into subgroups according to what sector they are in.",
                correct = TRUE, message = "You can use any number of variables to define groups."),
         answer("It chooses one or the other of sex or sector to form the groups.", 
                message = "That would not be good. Why should it do the choosing? You are the one who determines what the computer is going to do, not the other way around."),
         answer("It provides two different groupings: one by sex and a separate one by sector, so that summarise() can give two separate reports.", 
                message = "No. Note that each sex is subdivided into each of the sectors; it's not a separate list of the two sexes and the 8 sectors."),
         allow_retry = TRUE,
         random_answer_order = TRUE)
```




