---
title: "Data Computing: Chapter 4"
output: html_document
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(tutor)
library(ggplot2)
library(dplyr)
library(checkr)
library(DataComputing)
library(mosaicData)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

## Problem 4.1

For this course, most data will come to you in data-table form. But there are several ways that the data might be provided:

* As data from an R package. Many R packages, including `ScientificProgramming`, provide data tables as part of the package. To access these tables, you can load the package. (In these DataCamp exercises, this has often been done for you.)
* As a file. Data-table files come in many different types. The type is often indicated by the last part of the name (the "filetype extension"). Three common types are:
    - a specialized spreadsheet file, e.g. `.xmlx` in the Excel system.
    - a generic spreadsheet file, often a `.csv` (comma-separated values).
    - a highly efficient format provided by R with file endings like `.rda` or `.Rdata`.

You refer to a table from a package by name, **not in quotes**. The name has to be a legal R object name. The name will **not** end with a filename extension such as `.csv` or `.Rda`.

You refer to a data file by a name also, **always in quotes**. The name often consists of many parts, separated by dashes. 

* Files available over the internet have names beginning with something like `http://` and end with extensions like `.csv` or `.Rdata`, etc.
* Files on your own computer (or on your account in the RStudio server) often start with `/` or `./` or `~/` and end with `.csv` or `.Rdata`, etc.


```{r DC-chap-four-1, echo=FALSE}
question('Which of the following is a data table identified by `"http://tiny.cc/dcf/CountryCodes.rda"`.',
  answer("A file on my computer.", message = "Think where you see names started with `http://`" ),
  answer("A file available through the internet", correct = TRUE),
  answer("A file provided by a package.", message = "Packages provide data with commands like `data()`."),
  allow_retry = TRUE,
  random_answer_order = TRUE
)
```

## Problem 4.2

In the exercises and other activities for *Data Computing*, you will often see instructions like this:

> Use the `BabyNames` data table to ...

Note that the name is not in quotes, suggesting that it is a data table provided by a package. Unfortunately, you can't tell just from the name what package it is. If in doubt, one way to figure out which package provides the data table is with the `??` help notation, e.g.
```r
??BabyNames
```

It's also possible to refer to package data by explicitly naming the package, like this:

> Use the `DataComputing::BabyNames` data table to ...

The name before the double colons is the package name. The data table name follows the double colons. 

In order to use a data table from a package, you should either attach the package (with the `library()` command) or use the `data()` function. So either

    library(DataComputing)
    # ... or ...
    data(BabyNames, package = "DataComputing")


Either way, you will have access to the data table by name (e.g. `BabyNames`). It is not quoted, even though the name of the package is in quotes. I prefer the second style, because it explicitly documents where the data table is coming from.

In this exercise, you will:

1. Use `??CPS85` to figure out what package the `CPS85` data table comes from. You'll have to run this command to figure out the package name. Then you can fill in the blanks for (2) and (3).
2. Use `data()` to bring the `CPS85` data table into your session.
3. Use `head(CPS85)` to look at the first few lines of `CPS85`.

```{r, DC-four-2, exercise = TRUE, echo = FALSE}
??CPS85
data(_____, _____)
head(_____)
```

```{r DC-four-2-hint, echo = FALSE}
# The CPS85 data table comes from the "mosaicData" package.
# Remember the quotes when referring to "mosaicData"
```

```{r DC-four-2-soluton, echo = FALSE, results = "hide"}
data(CPS85, package = "mosaicData")
head(CPS85)
```

```{r DC-four-2-check}
test_0 <- find_call("data(CPS85, whatever)", "the first argument to `data()` is the data table, e.g. `CPS85`")
test_1 <- find_call("data(whatever, whatever)", "the second argument to `data()` is `package =`")

test_2 <- find_names(data(CPS85), "remember to use the data() function to access CPS85.")
test_3 <- check_argument("data(CPS85, package = grab_this)", 
                         test = agrees(is.character(x), 
                                       "the name of the package should be in quotes."))
test_4 <- find_constants("mosaicData", message = "the package containing the data is \"mosaicData\"")
test_5 <- find_call("data(whatever, package = 'mosaicData')", message = "argument should be the name of the package (in quotes).")
test_6 <- find_call("head(CPS85)", "give the data table as the argument to `head()`")

USER_CODE %>% test_0 %>% test_1 %>% test_2 %>% test_3 %>%  test_4 %>% test_5 %>% test_6
# and this isn't working either
# soln_test(USER_CODE, SOLN_CODE,
#              res = final_,
#              same_num(nrow(res)), hint = TRUE)
```


```{r echo = FALSE, eval = FALSE}
# For reference, the solution correctness test
test_student_typed("data(", not_typed_msg = "Remember to use the `data()` function.")
test_student_typed("CPS85", not_typed_msg = "Did you ask for `CPS85` (and spell it correctly?")
test_student_typed("package *= *\"mosaicData\"", fixed = FALSE, 
                   not_typed_msg = "Remember to give the name of the mosaicData package in quotes.")
success_msg("Good.")
```

## Problem 4.3

When you read a `.csv` or `.xlmx` spreadsheet file, you need to create a name by which to refer to the resulting data table.

Some tips:

* Remember that the name of the file goes in quotes.
* Use ordinary assignment, e.g. `My_table <- ` to give a name to the  data table that will be created.
* Use `read.csv()` for `.csv` files and `readxl::read_excel` for `.xlsx` files.


Read in the file `"http://tiny.cc/dcf/CountryCodes.csv"` and name the resulting object `CCodes`.

```{r DC-four-3, exercise = TRUE}
# your statement goes here
```

```{r DC-four-3-solution, echo = FALSE}
CCodes <- read.csv("http://tiny.cc/dcf/CountryCodes.csv")
```

```{r DC-four-3-hint, echo = FALSE}
# Use the `read.csv()` function and make assignment to `CCodes`
```

```{r DC-four-3-check, echo = FALSE}
test_1 <- find_call("read.csv(whatever)")
test_2 <- find_statement("[\"'].*[\"']", 
                        message = "you don't have the file name in quotes.",
                        regex = TRUE)
test_3 <- find_constants("http://tiny.cc/dcf/CountryCodes.csv", 
                        message = "you don't have the name of the file typed correctly.")
test_4 <- find_assignment("CCodes", message = "remember to assign the output to `CCodes`.")
USER_CODE %>% test_1 %>% test_2 %>% test_3 %>% test_4
```

```{r echo = FALSE, eval = FALSE}
# DataCamp submission correctness tests
test_student_typed('http://tiny.cc/dcf/CountryCodes.csv"',
                    not_typed_msg = "Remember the entire file name must be given, in quotes.")
success_msg("There are several other functions for reading CSV and other forms of file, but we don't need to use them in the next several chapters.")
```

There are several other functions for reading CSV and other forms of file, but we don't need to use them in the next several chapters.



