---
title: "Data Computing: Chapter 8"
output: html_document
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(tutor)
library(ggplot2)
library(dplyr)
library(checkr)
library(DataComputing)
library(mosaicData)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

# Problem 8.1: Making a graphics frame

In previous exercises, you used a formula-based interface to the `ggplot2` system for graphics. That formula-based interface is intended to be easy for getting started with making simple graphics. In these exercises, you'll practice with the `ggplot` interface itself.

The `ggplot()` function is used to define a the graphics frame. The frame it makes is blank, ready to have additional layers of glyphs added to it. The typical arguments to `ggplot()` are:

1. A data table, given as the first argument or piped into `ggplot()`.
2. An `aes()` statement which constructs the mapping from variables in the data table to the `x` and `y` aesthetics, that is, the frame itself.


```{r echo = FALSE}
data(CountryData, package = "DataComputing")
library("ggplot2")
library("dplyr")
CountryData %>% ggplot(aes(x = death, y = life))
```

The graphic above shows a (blank) frame constructed by `ggplot()`. We'll add layers to this blank frame in the exercises that follow, but for now your task is simple: re-create the blank frame.

Read from the graph the variables that have been mapped to the x and y aesthetics.
Fill in the blanks in order to construct a command that will reproduce the blank frame.

```{r DC-eight-1, exercise = TRUE}
# Provide access to CountryData
data(CountryData, package = "DataComputing")

# Attach the ggplot2 package
library("ggplot2")

# Fill in the blanks ...
CountryData %>%
  ggplot(aes(x = ___, y = ___))
```

- Read from the graph the variables that have been mapped to the x and y aethetics.
- Fill in the blanks in order to construct a command that will reproduce the blank frame.

*** =solution
```{r DC-eight-1-solution, echo = FALSE}
data(CountryData, package = "DataComputing")
library("ggplot2")
CountryData %>% ggplot(aes(x = life, y = death))
```

```{r DC-eight-1-hint, echo = FALSE}
As you can see, `life` is being mapped to the x aesthetic, `death` to the y aesthetic. It will seem a bit odd at first, but remember to use `aes()` as a function, given as an argument to `ggplot()`, and map the aesthetics by giving appropriate arguments to `aes()`.

```{r DC-eight-1-check, echo = FALSE}
set_success_message("Good. A blank frame isn't good for much. We'll add glyphs, labels, and such in the exercises that follow.")
test_1 <- any_test(find_call("ggplot(x = whatever)"), find_call("ggplot(y = whatever)"))
USER_CODE %>% test_1 %>% 
  was_mistake("remember that aesthetics drawn from variables must be placed as arguments to the `aes()` function, which itself will be an argument to `ggplot()`. ")
test_2 <- find_call("aes(x = whatever, y = whatever)", "set both x and y aesthetics within a call to `aes()`.")
test_3 <- find_call("aes(y = life)", 
  message = "look again at the graphic to see which variable is being mapped to the y axis.")
test_4 <- find_call("aes(x = death)", "are you sure you've mapped the right variable to the x axis?")
test_5 <- check_value(test = agrees(inherits(x, "ggplot")))
USER_CODE %>% test_2 %>% test_3 %>% test_4 %>% final_ %>% test_5
```

## Adding a layer

## Faceting

## Mapping an aesthetic in the layer

## Adding x- and y-axis labels


## Hints from the formula interface

How to get the formula interface to print out the corresponding ggplot command.

