---
title: "DC-2016-12-30-a163b"
output: html_document
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

```{r DC-2016-12-30-a163b-setup, echo = FALSE}
# code to be evaluated before exercise code
library(ggplot2)
set.seed(101)
diamonds <- diamonds %>% dplyr::sample_n(size = 2000)
```

In your work with *Data Computing*, you will be using the `ggplot2` package for making graphics.  The code pane contains commands to show a few lines from a data table named `diamonds` and to make a plot of price against size (`carat`) for different cuts of diamonds.

Read through the commands in the code pane. Then press "Run Code". Once you understand how the output is related to the commands themselves, modify the `ggplot()` command so that the `clarity` variable is used instead of `cut`. 

```{r DC-2016-12-30-a163b, exercise = TRUE, exercise.setup = "DC-2016-12-30-a163b-setup", exercise.eval = FALSE}
# Show the first few lines of the data table
head(diamonds)

# Plot out some of the data
ggplot(diamonds, 
       aes(x = carat, y = price, color = cut)) + 
  geom_point()
```

<!-- narrative to wrap up (if any) goes here -->

```{r DC-2016-12-30-a163b-hint, echo = FALSE}
# The phrase `color = cut` instructs `ggplot()` to 
# set the color of each dot according to the value of the variable `cut`.
# So change `cut` to `clarity`.
```

```{r DC-2016-12-30-a163b-solution, echo = FALSE}
ggplot(diamonds, 
       aes(x = carat, y = price, color = clarity)) + 
  geom_point()
```

```{r DC-2016-12-30-a163b-check, echo = FALSE}
set_success_message("Good job!") # change as you like
test_1 <- find_call("aes(color = clarity, x = whatever, y = whatever)", "check the name of the variable that's being mapped to the `color` argument to the `aes()` function.")
USER_CODE %>% test_1
```


