---
title: "DC-2017-02-03-4a876"
output: html_document
runtime: shiny_prerendered
---

```{r include=FALSE}
library(tutor)
library(checkr)
knitr::opts_chunk$set(exercise.checker = checkr::checkr_tutor)
```

CHANGE THIS PROPORTION-Counting into a join operation. Create an auxiliary table which finds the total number of babies born each year. Then join this to the Mary/Jane table.


### 3. Look at the *proportion* of births rather than the count

In the previous item you graphed the number of babies each year. Here, you should modify things so that 

```{r DC-2017-02-03-293cb-2, exercise = TRUE, exercise.eval = FALSE}
Result2 <-
  BabyNames %>%
  group_by(year) %>%
  mutate(total = ????(count)) %>%
  filter(????) %>%
  mutate(proportion = ???? / ????)
# Then add your plot command

```

* Why is `sex` a variable in `Result2`? Eliminate it, keeping just the girls.
    Note: It would likely be better to add up the boys and girls, but this is surprisingly hard.  It becomes much easier once you have another data verb to work with: `inner_join()`.  
* What happens if the `filter()` step is put *before* the `mutate()` step?

Just as you did with count vs year, graph proportion vs year.
```{r eval=FALSE}
Result2 %>%
  Your ggplot statements go here!
```



```{r DC-2017-02-03-4a876-setup, echo = FALSE}
# code to be evaluated before exercise code
```

<!-- narrative before exercise -->

```{r DC-2017-02-03-4a876, exercise = TRUE, exercise.setup = "DC-2017-02-03-4a876-setup", exercise.eval = FALSE}
sqrt(17) # Starting code for exercise
```

<!-- narrative to wrap up (if any) goes here -->

```{r DC-2017-02-03-4a876-hint, echo = FALSE}
# hint text or code. Can offer multiple hints with similar chunks ending in hint-1, hint-2, etc.
```

```{r DC-2017-02-03-4a876-solution, echo = FALSE}
# code or text that's a solution to the exercise
```

```{r DC-2017-02-03-4a876-code-check, echo = FALSE}
# put pre-evaluation checking here. This can be blank, in which case
# the code will be checked by the interpreter with the usual R error messages
# shown in the even of a problem.
check_blanks(USER_CODE)
```

```{r DC-2017-02-03-4a876-check, echo = FALSE}
set_success_message("Good job!") # change as you like
test_1 <- final_ # replace with your own
USER_CODE %>% test_1
```

<!-- identifier for the source problem file is the tooltip on the "+" below. -->
<a href="#" title = "DC-2017-02-03-4a876">+</a>

